\newcommand{\ZZ}{\mathbb{Z}} % The Integers
\newcommand{\vspan}{\text{span}} % the span of vectors
%
%
Consider the general Schmidt decomposition for a bipartite system:
$$
\cos\theta \ket{\alpha_0} \ket{\beta_0} + 
\sin\theta \ket{\alpha_1} \ket{\beta_1}
$$
Following convention, the Schmidt coefficients are non-decreasing: so $\theta \in [0, \pi/4)$. Clearly, $\theta = 0$ corresponds to zero entanglement, while $\theta = \pi/4$ corresponds to maximal entanglement.

We demand that the entanglement occur only pairwise, and that each pair be entangled to the same degree. Since entanglement entropy is a non-decreasing function of $\theta$, each pair must therefore have the same Schmidt coefficients.

Therefore, the Schmidt decomposition of the $i^{\text{th}}$ pair is  
$$
\cos\theta \ket{\alpha_0(i)} \ket{\beta_0(i)} + 
\sin\theta \ket{\alpha_1(i)} \ket{\beta_1(i)}
$$

And the total state of the system is
\begin{align}
	\ket{\psi} &= \bigotimes_{i=1}^n \left( 
	\cos\theta \ket{\alpha_0(i)} \ket{\beta_0(i)} + 
	\sin\theta \ket{\alpha_1(i)} \ket{\beta_1(i)} \right) \\
	%
	&= \sum_{k=0}^n \cos^{n-k}\theta \sin^k\theta
	\sum_{x \in H(k)} \bigotimes_{i=1}^n 
	\ket{\alpha_{x_i}(i)} \ket{\beta_{x_i}(i)} \\
	%
	&=  \sum_{k=0}^n \cos^{n-k}\theta \sin^k\theta
	\sum_{x \in H(k)} \ket{\phi_x}
\end{align}

Where 
$$
H(k) = \left\{ 
x \in \ZZ_2^n : \text{the Hamming Weight of $x$ is $k$} 
\right\}
$$

and
$$
\ket{\phi_x} = \bigotimes_{i=1}^n 
\ket{\alpha_{x_i}(i)} \ket{\beta_{x_i}(i)}
$$


Since $ \braket{\alpha_j(i)}{\alpha_k(i)} = \braket{\beta_j(i)}{\beta_k(i)} = \delta_{jk} $, we have that $\braket{\phi_x}{\phi_y} = \delta_{xy}$.
Therefore $V_k = \vspan(\ket{\phi_x} : x \in H(k))$ is a subspace of the full Hilbert space with dimension $\binom{n}{k}$.
Furthermore the $V_k$ are orthogonal to each other.

Let Alice perform a von Neumann measurement that projects the state into one of these $V_k$ subspaces. That is, let Alice to measure the observable $A_H$
$$
A_H = \sum_{k=0}^n k \left( \sum_{x \in H(k)}  \dyad{\phi_x}{\phi_x} \right) 
$$

Alice can communicate her result to Bob over a classical channel, or she can let Bob perform his own $A_H$ measurement: by virtue of the entanglement their results will always agree.

The resulting state is
\begin{equation}
\label{eqn:kstate}
\ket{k} = \binom{n}{k}^{-1/2} \sum_{x \in H(k)} \ket{\phi_x}
\end{equation}

And it occurs with probability
$$
p_k = \binom{n}{k} \cos^{2(n-k)}\theta \sin^{2k}\theta
$$

$\ket{k}$ is a maximally entangled state in the $\binom{n}{k}^2$ dimensional subspace 
$$\vspan\left(\bigotimes_{i=1}^n 
\ket{\alpha_{x_i}(i)} \ket{\beta_{y_i}(i)}: x,y \in H(k)\right)
$$
This is clear because the Schmidt coefficients \eqref{eqn:kstate} are uniform.
What remains is to convert this entanglement into maximally entangled qubits that can be used by standard quantum protocols. 

Let us repeat the procedure so far $m$ times. The result is a sequence of k values $\{k_1, k_2,\ldots k_m \}$, and the state
$\ket{K}$ is maximally entangled.
\begin{align}
\ket{K} &= \bigotimes_{\mu=1}^m \ket{k_\mu} \\
&= D_m^{-1/2} \bigotimes_{\mu=1}^m \sum_{x^\mu \in H(k_\mu)} \ket{\phi_{x^\mu}} \\
\label{eqn:Kstate}
&=  D_m^{-1/2} \sum_{x^1 \in H(k_1)} \cdots \sum_{x^m \in H(k_m)} \bigotimes_{\mu=1}^m  \ket{\phi_{x^\mu}}
\end{align}
Similarily to the $m=1$ construction, we treat $\ket{K}$ as a member of the $D_m^2$ dimensional subspace $W_K$
\begin{equation}
D_m = \prod_{\mu=1}^{m} \binom{n}{k_\mu}
\end{equation}
\begin{equation}
\label{eqn:Wk}
W_K = \vspan\left(\bigotimes_{\mu=1}^m\bigotimes_{i=1}^n 
\ket{\alpha_{x_i^\mu}(i)} \ket{\beta_{y_i^\mu}(i)}: x^\mu,y^\mu \in H(k_\mu)\right)
\end{equation}
Since \eqref{eqn:Kstate} is the Schmidt decomposition of $\ket{K}$, $\ket{K}$ is maximally entangled in $W_K$.

If $D_m = 2^l$ for some integer $l$ then we are done. To see this we label the basis vectors numerically
\begin{align}
\left\{
\bigotimes_{\mu=1}^m\bigotimes_{i=1}^n 
\ket{\alpha_{x_i^\mu}(i)}: x^\mu \in H(k_\mu) 
\right\} &= \{a_1, \ldots a_{2^l}\} \\
\left\{
\bigotimes_{\mu=1}^m\bigotimes_{i=1}^n 
\ket{\beta_{x_i^\mu}(i)}: x^\mu \in H(k_\mu) 
\right\} &= \{b_1, \ldots b_{2^l}\} 
\end{align}
and reorder the product states so that all the states belonging to Alice are on the right and all the states belonging to Bob are on the left. Then
\begin{equation}
	\ket{K} = 2^{-l/2}\sum_{i=1}^{2^l} \ket{a_i}\ket{b_i}
\end{equation}


\subsection{Entropy}
The starting entanglement entropy is

